---
title: "Player Scouting Report"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
params:
  params_rds: "PLACEHOLDER"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(tidyr)
`%||%` <- function(a, b) if (!is.null(a)) a else b
dat <- readRDS(params$params_rds)
p <- dat$player
cutoff <- dat$cutoff_label %||% p$data_cutoff_label %||% "Cutoff unknown"
period_lab <- p$season_label %||% "Evaluation period not specified"
is_syn <- isTRUE(dat$provenance$is_synthetic) || isTRUE(p$is_synthetic)
```

# `r p$display_name`

**Internal scouting document — decision support only**

```{r banner}
if (is_syn) {
  cat("**SYNTHETIC DEMO DATA — NOT A GENUINE SCOUTING REPORT**\n\n")
} else {
  cat(paste0("**", cutoff, "**  \n"))
  cat(paste0("**Evaluation period:** ", period_lab, "  \n"))
  if (!isTRUE(p$stats_are_full_season)) {
    cat("**Note:** Any 2026 statistics are season-to-date, not full-season.\n\n")
  }
}
```

| Field | Detail |
|------|--------|
| Current competition | `r toupper(p$league_id)` |
| Age | `r p$age` |
| Position group | `r p$position_group` |
| Evaluated role | `r p$role_id` |
| Minutes (period) | `r round(p$minutes)` |
| Confidence | `r p$confidence` |
| Data quality | `r round(p$data_quality)` |
| Data cutoff | `r cutoff` |

## Statistical profile

Projected MLS proxies (per 90, translated):

- nPxG: **`r round(p$proj_npxg_p90, 3)`**
- xA: **`r round(p$proj_xa_p90, 3)`**
- Goals Added: **`r round(p$proj_gplus_p90, 3)`**

```{r radar-bar}
scores <- tibble::tibble(
  component = c("Projected MLS", "Role fit", "Feasibility", "Development", "Financial value", "Risk"),
  value = c(p$score_projected_mls, p$score_role_fit, p$score_feasibility,
            p$score_development, p$score_financial_value, p$score_risk)
)
ggplot(scores, aes(reorder(component, value), value, fill = component)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Component scores (0–100)", x = NULL, y = NULL) +
  theme_minimal(base_size = 12)
```

## Projected MLS performance

Overall projected contribution score: **`r round(p$score_projected_mls, 1)`**.  
Interpretation reflects league translation priors, sample-size shrinkage, and age context. This is **not** a guaranteed MLS outcome.

## Acquisition feasibility

Feasibility score: **`r round(p$score_feasibility, 1)`** (cost tier `r p$cost_tier`).  
Treat as a public-data attainability prior; confirm contract/roster reality with football ops.

## Financial-value assessment

Financial value score: **`r round(p$score_financial_value, 1)`**.  
Surplus is standardized contribution versus estimated cost tier/salary — not a literal NPV in dollars.

## Development upside

Development score: **`r round(p$score_development, 1)`**.  
Factors: age vs positional peak, YoY signal, minutes trajectory.

## Main strengths

`r p$strengths`

## Main risks

`r p$risks_text`

## Video scouting questions

`r p$video_questions`

## Recommendation

```{r rec}
rec <- dplyr::case_when(
  p$score_feasibility < 30 ~ "Pass",
  p$score_overall >= 70 & p$score_risk <= 45 ~ "Pursue",
  p$score_development >= 70 & p$score_overall >= 55 ~ "Development target",
  p$score_overall >= 55 ~ "Monitor",
  TRUE ~ "Pass"
)
```

### **`r rec`**

Overall score: **`r round(p$score_overall, 1)`** (risk `r round(p$score_risk, 1)`).

---

*Methodology and limitations: `docs/methodology.md`, `docs/limitations.md`.*
