---
title: "Recruitment Shortlist Memo"
output:
  html_document:
    theme: flatly
params:
  params_rds: "PLACEHOLDER"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
dat <- readRDS(params$params_rds)
sl <- dat$shortlist
```

# Shortlist memo (10–15 targets)

**Classification:** Internal sporting strategy — public-data decision support  
**Run note:** Club-conditioned rankings from MLS Recruitment Intelligence MVP

This memo prioritizes **attainable and undervalued** profiles within a defined tactical role — not a global talent ranking.

```{r table}
sl |>
  dplyr::group_by(club_id) |>
  dplyr::slice_head(n = 15) |>
  dplyr::ungroup() |>
  dplyr::transmute(
    Club = club_id,
    Rank = rank,
    Player = display_name,
    League = toupper(league_id),
    Age = age,
    Role = role_id,
    Overall = round(score_overall, 1),
    RoleFit = round(score_role_fit, 1),
    Feasibility = round(score_feasibility, 1),
    Value = round(score_financial_value, 1),
    Upside = round(score_development, 1),
    Risk = round(score_risk, 1),
    Rec = recommendation
  ) |>
  knitr::kable()
```

## Process notes

1. Players cleared a minimum-minutes threshold and role filter.  
2. League translation used transparent tier priors (see `config/league_tiers.yml`).  
3. Cost used salary/cost tiers; transfer fees remain uncertain.  
4. Final signing decisions require video, medical, and roster-rule validation.

## Suggested next actions

- Film 3–5 **Pursue** targets this week.  
- Soft-monitor **Development target** names for minutes/form.  
- Drop **Pass** names unless price/availability changes materially.
